Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-05-22 article.rnw
Add an additional reference regarding species interaction models usually being small.

Making practical use of a model requires experimentally or observationally determining the values of each of the model's parameters.
This poses a particular problem for models that include species interactions due to the sheer number of parameters that must be determined.
Even the simplest models with no environmental dependence require one parameter to characterise the interaction of each pair of species \parencite{novak2016characterizing, rocha2005lotka}.
% DBS: Hmm. Should the above two or rephrased to embrace the directionality of what's going on?
Hence the number of parameters scales quadratically with the number of species; at least \num{100} parameters are required for the interactions in a community of ``just'' \num{10} species.
Determining these parameters experimentally requires at least one experiment per parameter, and preferably more \parencite{hart2018quantify}.
This is understandably expensive and requires substantial effort.
As such, model-based predictions of real communities are typically restricted to a small number of focal species \parencite{ovaskainen2017species, XXX}.
However, real communities can contain hundreds of species \parencite{cornell1999unsaturation}, or even thousands for microbial communities assessed by genetic metabarcoding \parencite{warton2015variables}.
To bridge this gap between the size of real communities and our ability to parameterise models for them, we need an ecologically-defensible way to reduce the number of parameters that predictive models require.

>>>>

Making practical use of a model requires experimentally or observationally determining the values of each of the model's parameters.
This poses a particular problem for models that include species interactions due to the sheer number of parameters that must be determined.
Even the simplest models with no environmental dependence require one parameter to characterise the interaction of each pair of species \parencite{novak2016characterizing, rocha2005lotka}.
% DBS: Hmm. Should the above two or rephrased to embrace the directionality of what's going on?
Hence the number of parameters scales quadratically with the number of species; at least \num{100} parameters are required for the interactions in a community of ``just'' \num{10} species.
Determining these parameters experimentally requires at least one experiment per parameter, and preferably more \parencite{hart2018quantify}.
This is understandably expensive and requires substantial effort.
As such, model-based predictions of real communities are typically restricted to a small number of focal species \parencite{ovaskainen2017species,maynard2020predicting}.
However, real communities can contain hundreds of species \parencite{cornell1999unsaturation}, or even thousands for microbial communities assessed by genetic metabarcoding \parencite{warton2015variables}.
To bridge this gap between the size of real communities and our ability to parameterise models for them, we need an ecologically-defensible way to reduce the number of parameters that predictive models require.
